
\chapter{Introduction}

\section{Problem Statement}
Nowadays, \textbf{Google} is widely used to perform a variety of information retrieval, with undoubtedly relevant results. However, in the field of domain-specific knowledge (e.g. education, health care,...) it is only able to find very general knowledge, and often requires users to do extensive searching. Therefore, our group aims to build a virtual assistant, coupled with a tailored knowledge base, guiding a user through a number of questions, learning their preferences and present the most relevant results. Moreover, as we collect sensitive user information, there is a need to securely store them in a way that prevents tampering and unauthorized usage.

\section{Goals}

The goals of the project
\begin{itemize}
    \item Implement an application on cross-platform mobile technology in order to fasten and optimize the cost of building application on platform-specific versions
    \item Construct a virtual assistant (in the form of a chatbot) to assist users to find relevant information about studying abroad. The results will then be analyzed to recommend better options for the user, based on their preferences.
    \item Securely store the collected data, prevent third-party sniffing and unauthorized usage of said data for monetary motives.
\end{itemize}
	

Based on the goals that have been specified, the progress of this project is divied into n phases:
\begin{itemize}
    \item Phase 1: Conversational assistant + Recommendation System
    \item Phase 2: Blockchain integration
\end{itemize}

\section{Scopes}
    This project aims to create a mobile application using React Native framework with a chatbot using Rasa framework to recommendation purposes on specific domain such as education. And we also collect user information for learning about the users to bring them more relevant contents.
    Because of the limited access to data for recommendation, the system may not respond with the most relevant results.
\newpage
\section{Thesis Structure}
\begin{tabular}{|c|p{10cm}|} 
    \hline
    Chapter & Content \\
    \hline
    1 & Brief introduction of the thesis and the project plan.\\
    \hline 
    2 & Introduction of theoretical knowledge and technologies that are used in the project.\\
    \hline
    3 & Introduction of the design structure of the project.\\
    \hline 
    4 & Summary of the project and the future plan.\\
    \hline
\end{tabular}
