\chapter{Summary}
\section{Thesis Status}
\subsection{Chatbot}

Chatbot has been implemented and operated to answer a few questions to meet the demand of searching on the field of study abroad. The basic structures of chatbot including intents, entities, slots, actions have been built and ready for further expansion. In addition, chatbot can now deloy onto mobile apps via API.
\subsection{Mobile App}

Up to now, the mobile app has been able to work well on a execution flow including registration, login, search and chat with chatbot to receive search results, implemented by React Native and runs well on both Android and IOS. A number of mobile extension functions are being researched, including automatic login, scanning of personal information from identity cards, etc.
\section{Future Improvement}

In the next time, we will improve the system according to the following plan
\begin{itemize}
\item Enhancing training for chatbot, helping it to better understand users' languages
\item Add many plugins for chatbot to make conversations easier and more interesting
\item Improve the response speed of chatbot
\item Increasing performance as well as reducing the size of the mobile app
\item Added the ability to collect information of users to serve the recommender system in the future
\item Researching and developing algorithms and preparing databases for recommender system
\item Expand the fields that chatbot can meet
\item Integrating functions related to device control to make chatbot easy to become a trusted virtual assistant
\item Research and apply blockchain in storing personal data of users
\end{itemize}

\section{Future Development}

In the near future, we plan to perfect the system including:
\begin{itemize}
\item A mobile app that completes the execution of the flow, can work well on Android and IOS.
\item Chatbot integrated in the mobile app, which can serve in search of certain areas and serve as a virtual assistant for users.
\item Recommender system to provide product recommendations that are suitable for users through data collected from chatbots, and acts as a link between users and service providers.
\item The system helps store and secure user information through blockchain.
\end{itemize}